Reducing Acceptance Marks \\ in Emerson-Lei Automata

### 2021-10-14 paper/main.tex
small fixes and note in conclusion

The second technique is completely different. For a given TELA and
parameters $k,n$, it produces a \emph{quantified boolean formula
  (QBF)} which is satisfiable if and only if there exists an
equivalent automaton with the identical structure, $n$ acceptance
marks, and an acceptance formula in \todo{conjunctive?}  normal form
with $k$ clauses. The placement of the marks on transitions and the
acceptance formula can be obtained from a model of the
formula. Besides this formula, we describe also the construction of a
simpler formula such its satisfiability implies existence of an
equivalent automaton with the identical structure and $n$ acceptacne
marks, but not vice versa.

@@

>>>>

The second technique is completely different. For a given TELA and
parameters $c,m$, it produces a \emph{quantified boolean formula
  (QBF)} which is satisfiable if and only if there exists an automaton
with the same structure, $m$ acceptance marks, an acceptance formula
in disjunctive normal form with $c$ clauses, and the same set
of accepting runs. The placement of the marks on transitions and the
acceptance formula can be obtained from a model of the
formula. Besides this formula, we describe also the construction of a
simpler formula such its satisfiability implies existence of an
automaton with the same structure, $m$ acceptance marks, and the same
set of accepting runs, but not vice versa.

@@

chceme sem napsat, ze QBF-based reduction se da pouzit napr. k
nalezeni akceptacni formule s $c$ klauzulemi a $m$ znackami v CNF,
pripadne k nalezeni ekvivalentniho paritniho automat s danou maximalni
paritou $p$ a stejnou strukturou.
